Model Recognition as Planning

### 2018-11-17 doc/icaps-19/model-recognition.tex

\section{Related work}
\label{sec:related}
An intriguing research line related with {\em model recognition} is {\em model reconciliation}~\cite{ChakrabortiSZK17} where model edition is used to conform the PDDL models of two different agents wrt an observation of a plan execution. In {\em model recognition} we also conform every input model $\mathcal{M}$ in the $M$ set with another model $\mathcal{M}'$ s.t. it is consistent with the input observation. Note however that in the {\em model recognition} task, the model $\mathcal{M}'$ is not given as input but instead, this model $\mathcal{M}'$ is computed for every $\mathcal{M}\in M$. Further, {\em model recognition as planning} shows that two input planning models can be conformed using an off-the-shelf classical planner and wrt an observation of a planning execution that contains no information of the applied actions.

Once the planning model of the observed agent is recognized, then the model-based machinery for automated planning becomes fully applicable. Of course, this includes the current approaches for {\em goal recognition}~\cite{ramirez2012plan}, {\em goal recognition design}~\cite{KerenGK14} and {\em counter-planning}~\cite{pozanco2018counterplanning} that require to have a model, in advance and fixed, of the observed agent. Last but not least, our approach allows to predict the future actions of an observed agent whose behavior is not ruled by a deliberative planning process that aims to achieve certain goals. As an example, our experiments show that {\em model recognition} is suitable for anticipating the actions of agents that are ruled by the execution of a fixed program or a finite state machine, such as a {\em regular automata}.

>>>>

\section{Related work}
\label{sec:related}
An interesting research line related with {\em model recognition} is {\em model reconciliation}~\cite{ChakrabortiSZK17}. In {\em model reconciliation} model edition is used to conform the PDDL models of two different agents, or the model of an agent with a given {\em annotated model}~\cite{sreedharan2018handling}, and with respect to a fully observed {\em optimal plan} computed using one of the models. It can be thought that {\em model recognition} conforms every input model $\mathcal{M}$ in the $M$ set with another model $\mathcal{M}'$ s.t. it is {\em consistent} with a partial observation of a plan execution. Note however that in the {\em model recognition} task, the model $\mathcal{M}'$ is not given as input and instead, this model $\mathcal{M}'$ is computed for every $\mathcal{M}\in M$. Further, {\em model recognition as planning} shows that the probability of an input planning model to explain a partial observation of a plan execution (that contains no information of the applied actions and where intermediate states may be incomplete or even missing) can be estimated with an off-the-shelf classical planner.

Once the planning model of the observed agent is recognized, then the model-based machinery for automated planning becomes fully applicable. Of course, this includes the current approaches for {\em goal recognition}~\cite{ramirez2012plan}, {\em goal recognition design}~\cite{KerenGK14} and {\em counter-planning}~\cite{pozanco2018counterplanning} that require to have a model, in advance and fixed, of the observed agent. Last but not least, our approach allows to predict the future actions of an observed agent whose behavior is not ruled by a deliberative planning process that aims to achieve certain goals. As an example, our experiments show that {\em model recognition} is suitable for anticipating the actions of agents that are ruled by the execution of fixed programs or finite state machines, such as a {\em regular automata}.
